---
title: "PS1_ECON_471"
author: "kareem2, alynde2, luigi2"
date: "2023-02-02"
output:
  pdf_document:
  extra_dependencies: 'amsmath'
  keep_tex: yes
---

### 2.3 Writing Funcitons to Calculate Conditional Distributions

```{r echo = TRUE, results='asis'}
library(data.table)
library(knitr)
#1
N = 100
#2
unif.draws = runif(N, 0, 1)
#3
data = data.table(unif.draws)
#4
data[unif.draws < .09, education := "Less than high school"]
data[unif.draws >= .09 & unif.draws < .37, education := "High school"]
data[unif.draws >= .37 & unif.draws < .62, education := "Some college"]
data[unif.draws >= .62 & unif.draws < .86, education := "College"]
data[unif.draws >= .86, education := "More than college"]
```

##### 5

unif.draws is analogous to an event or outcome in $\Omega$, and education is analogous to a variable which measures the event.

##### 6

The distribution of education is as follows \$

\
\$

             \begin{cases} 
              0.09 & education = \text{Less than high school} \\
              0.28 & education = \text{High school} \\
              0.25 & education = \text{Some college} \\
              0.24 & education = \text{College} \\
              0.14 & education = \text{More than college}
             \end{cases}
        $


```{r}
#7
data[education == "Less than high school", base.wages := 15.48]
data[education == "High school", base.wages := 19.53]
data[education == "Some college", base.wages := 22.50]
data[education == "College", base.wages := 32.63]
data[education == "More than college", base.wages := 41.25]

#8
data[, skill := rnorm(100, 0, 1)]

#9
data[, wage := base.wages + 5 * skill]

#10
mean(data$wage)
var(data$wage)

#11
mean(data$wage[data$education == "College"])
var(data$wage[data$education == "College"])
```

We can see here that the mean wage is higher given education = College
